---
title: "European football grounds"
author: "Sebastian Scherer"
date: "14 September 2019"
output: html_document
---

# {.tabset}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

The below map shows a selection of european football clubs' grounds across france, spain germany and the UK.

It also highlights the two clubs that I support:

1. AFC Wimbledon (UK, Football league)
2. Eintracht Frankfurt (Germany, Bundesliga)

## The code dependencies

```{r}
# loading dependencies
library(magrittr)
library(data.table)
library(dplyr)
library(leaflet)
```

## The data

```{r, echoe = FALSE,comment=''}
# loading data
football_grounds_data <- data.table::fread('C:/Users/bettmensch/Documents/Coursera/developing_data_products/week_2/european_grounds_data.csv',
                  data.table = FALSE) %>%
  dplyr::select(Latitude, Longitude, Team, League, Stadium, Capacity)

frankfurt_ground <- football_grounds_data %>%
  dplyr::filter(Team == 'Eintracht Frankfurt')

wimbledon_ground <- football_grounds_data %>%
  dplyr::filter(Team == 'AFC Wimbledon')

remaining_grounds <- football_grounds_data %>%
  dplyr::filter(!Team %in% c('Eintracht Frankfurt','AFC Wimbledon'))

# top 10 records
remaining_grounds[1:10,]
```

## The grounds map

We create the colour palette and some custom icon markers.

```{r pressure, fig.width=10, fig.height=10}
# create color palette for markers according to league
league_values <- football_grounds_data$League %>% unique() %>% .[order(.)]
pal <- leaflet::colorNumeric(c("red", "green", "blue"), 1:length(league_values))

# create custom markers for favourites
frankfurt_icon <- leaflet::makeIcon(
  'C:/Users/bettmensch/Documents/Coursera/developing_data_products/week_2/frankfurt_badge.png',
  iconWidth = 50,
  iconHeight = 50,
  iconAnchorX = 50/2,
  iconAnchorY = 50/2
)

wimbledon_icon <- leaflet::makeIcon(
  'C:/Users/bettmensch/Documents/Coursera/developing_data_products/week_2/afc_wimbledon_badge.png',
  iconWidth = 44,
  iconHeight = 50,
  iconAnchorX = 44/2,
  iconAnchorY = 50/2
)

favourite_icons <- c(frankfurt_icon,wimbledon_icon)
```

Look at all these footbal grounds!

```{r,echo = FALSE,fig.width = 10, fig.height = 9}
grounds_map <- leaflet::leaflet(data = remaining_grounds) %>%
  leaflet::addTiles() %>%
  leaflet::addCircleMarkers(color = pal(remaining_grounds$League),
                            radius = ~Capacity/10000,
                            label = paste(remaining_grounds$Stadium,'
                                          (',
                                          remaining_grounds$Capacity,
                                          ';',
                                          remaining_grounds$Team,')')
  ) %>%
  leaflet::addMarkers(lat = frankfurt_ground$Latitude,
                      lng = frankfurt_ground$Longitude,
                      label = paste(frankfurt_ground$Stadium,'
                                          (',
                                          frankfurt_ground$Capacity,
                                          ';',
                                          frankfurt_ground$Team,')'),
                      icon = frankfurt_icon) %>%
  leaflet::addMarkers(lat = wimbledon_ground$Latitude,
                      lng = wimbledon_ground$Longitude,
                      label = paste(wimbledon_ground$Stadium,'
                                          (',
                                          wimbledon_ground$Capacity,
                                          ';',
                                          wimbledon_ground$Team,')'),
                      icon = wimbledon_icon) %>%
  leaflet::addLegend(position = "topright", 
                     colors = pal(league_values),
                     values = league_values,
                     title = 'League',
                     labels = league_values)#, values, na.label = "NA", bins = 7, colors,
  #opacity = 0.5, labels = NULL, labFormat = labelFormat(),
  #title = NULL, className = "info legend", layerId = NULL,
  #group = NULL, data = getMapData(map))

grounds_map
```