---
title: "week_2_project_webpage"
author: "Sebastian Scherer"
date: "14 September 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My new slide

Plain text

*italized text*

**Bold text**

`for (i in 1:10)`

Some content

## My title of the second new slide

- Bullet one
- Bullet two

1. Item a
2. Item b

### A top level subheading

#### A second level subheading

## My third new slide

```{r, comment = ''}
head(mtcars)
```

***
A slide without a title

## My fifth new slide

```{r,fig.align='center',fig.cap='My AWESOME figure'}
plot(mtcars$wt, mtcars$mpg, xlab = 'Weight', ylab = 'MPG')
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

