---
title: "Week 3 presentation project"
author: "Sebastian Scherer"
date: "23 September 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The *mpg* and *cyl* relationship in the **mtcars** data set

In this presentation, we will have a look at the features

- `mpg`
- `cyl`

from the `mtcars` data set (32 observations) and how they relate to one another. We will do this by showing some univariate and bivariate plots. The content of this presentation is as follows:

1. Package dependencies
2. Univariate box plot: Miles per gallon
3. Univariate bar chart: Number of cylinders
4. Bivariate stats

## Package dependencies

We will need the following packages.

```{r,results='hide'}
library(tidyverse)
library(plotly)
library(magrittr)
```

## Univariate box plot: Miles per gallon

### Code

```{r}
plot <- mtcars %>% 
  plotly::plot_ly() %>%
  plotly::add_boxplot(x = ~mpg, name = 'Miles per gallon') %>%
  plotly::layout(title = 'Distribution of mpg')
```

## Univariate box plot: Miles per gallon

### Plot

```{r,echo = FALSE}
plot
```

## Univariate bar chart: Number of cylinders

### Code

```{r}
plot <- mtcars %>% 
  dplyr::group_by(cyl) %>%
  dplyr::summarise(cyl_count = n()) %>%
  plotly::plot_ly() %>%
  plotly::add_bars(y = ~cyl_count, x = ~cyl, name = 'Number of cylinders') %>%
  plotly::layout(title = 'Distribution of cyl')
```

## Univariate bar chart: Number of cylinders

### Plot

```{r,echo = FALSE}
plot
```

## Bivariate stats

### Code

```{r}
plot <- mtcars %>%
  dplyr::group_by(cyl) %>%
  dplyr::summarise(mean_mpg = mean(mpg),
                   var_mpg = var(mpg),
                   n_cyl = n()) %>%
  plotly::plot_ly(data = .,
                  x = ~cyl,
                  y = ~mean_mpg,
                  type = 'bar',
                  name = 'Miles per gallon',
                  error_y = list(array = ~var_mpg,
                                 color = '#000000')
                  ) %>%
  plotly::layout(title = 'Miles per gallon aggregated across number of cylinders')
```

## Bivariate stats

### Plot

```{r, echo = FALSE}
plot
```